Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
section

\begin{proof}
Since $\mathscr{S}$ is a WSTS there exists $n_0 \in \N$ such that
$\pred^*(\Safe) =  \pred^{\leq n_0}(\Safe)$. We can compute this $n_0$ by iteratively computing 
$\pred^{\leq n+1}(\Safe)$ from $\pred^{\leq n}(\Safe)$, checking 
$\pred^{\leq n+1}(\Safe) = \pred^{\leq n}(\Safe)$, 
returning $n$ if that is the case.
Then, because {\sc $n_0$-state-resilience} is decidable, 
checking $\uparrow \post^*(s) 
 \subseteq \pred^{\leq n}(\Safe) = \pred^*(\Safe)$ is,
and {\sc State-resilience} is decidable. \qed
\end{proof}

@@

%\"Ozkan
\begin{proposition}[Proposition 1 in \cite{DBLP:conf/gg/Ozkan22}]\label{post*}
For finite-branching WSTS, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
\end{proposition}

@@

\begin{proof}
Let $B_{\uparrow \post^*(s)}$ 
 be a basis of $\uparrow \post^*(s)$, $B_\Safe$ a basis of $\Safe$.
By applying Lemma~\ref{Lemma intersection} twice, we obtain
\[ \post^*(s) 
 \subseteq \pred^*(\Safe) \text{ iff } B_{\uparrow \post^*(s)}  
 \subseteq \pred^*(\Safe)\]
Since $B_{\uparrow \post^*(s)}$ is finite and we can compute a basis of $\pred^*(\Safe)$ from $B_\Safe$, we can check that $B_{\uparrow \post^*(s)} 
 \setminus \pred^*(\Safe) = \emptyset$.  \qed
\end{proof}

However when removing strong compatibility, precision is lost.
Since $\pred(\uparrow \Safe)$ is not necessarily upward-closed, it is possible to have 
 $\uparrow \post^* (s) \cap S \not\subseteq \pred(\Safe)$,
despite having 
$\post^* (s) \cap S \subseteq \pred( \Safe)$.
In such a case the algorithm from
\cite{DBLP:conf/gg/Ozkan22} would deduce that {\sc $1$-state-resilience} does not hold,
which is incorrect.

>>>>

\begin{proof}
Since $\mathscr{S}$ is a WSTS there exists an $n_0 \in \N$ such that
$\pred^*(\Safe) =  \pred^{\leq n_0}(\Safe)$. We can compute the least $n_0$ by iteratively computing 
$\pred^{\leq n+1}(\Safe)$ from $\pred^{\leq n}(\Safe)$, checking 
$\pred^{\leq n+1}(\Safe) = \pred^{\leq n}(\Safe)$, 
returning $n$ if that is the case.
Then, because {\sc $n_0$-state-resilience} is decidable, 
checking $\uparrow \post^*(s) 
 \subseteq \pred^{\leq n}(\Safe) = \pred^*(\Safe)$ is,
and {\sc State-resilience} is decidable. \qed
\end{proof}

@@

%\"Ozkan
\alain{pourquoi ne pas juste écrire Proposition 1 \cite{DBLP:conf/gg/Ozkan22}et enlever "notre" proposition 3 ?}
\begin{proposition}[Proposition 1 in \cite{DBLP:conf/gg/Ozkan22}]\label{post*}
For finite-branching WSTS, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
\end{proposition}

@@

\begin{proof}
Let $B_{\uparrow \post^*(s)}$ 
 be a basis of $\uparrow \post^*(s)$, and $B_\Safe$ a basis of $\Safe$.
By applying Lemma~\ref{Lemma intersection} twice, we obtain
\[ \post^*(s) 
 \subseteq \pred^*(\Safe) \text{ iff } B_{\uparrow \post^*(s)}  
 \subseteq \pred^*(\Safe)\]
Since $B_{\uparrow \post^*(s)}$ is finite and we can compute a basis of $\pred^*(\Safe)$ from $B_\Safe$, we can check that $B_{\uparrow \post^*(s)} 
 \setminus \pred^*(\Safe) = \emptyset$.  \qed
\end{proof}

However when removing strong compatibility, some precision is lost.
Since $\pred(\uparrow \Safe)$ is not necessarily upward-closed, it is possible to have 
 $\uparrow \post^* (s) \cap S \not\subseteq \pred(\Safe)$,
despite having 
$\post^* (s) \cap S \subseteq \pred( \Safe)$.
In such a case, the algorithm in
\cite{DBLP:conf/gg/Ozkan22} would deduce that {\sc $1$-state-resilience} does not hold,
which is incorrect.
